### 2023-10-15 sections/2-methods.tex
reworking data augmentation explanation

After the first $\log{\frac{n}{2k}}$ iterations, we have that the cardinalities of clusters in $Q$ are at most $2k$, at which point, based on our assumption, we have that the length of $Q$ is close to $2d$.
Therefore, the asymptotic complexity of the sieve algorithms is $\mathcal{O}\left(log(\frac{n}{d})\right)$.

>>>>

After the first $\log{\frac{n}{2k}}$ iterations, we have that the cardinalities of clusters in $Q$ are at most $2k$, at which point, based on our assumption, we have that the length of $Q$ is close to $2d$.
Therefore, the asymptotic complexity of the sieve algorithms is $\mathcal{O}\left(\log(\frac{n}{d})\right)$.

\subsection{Synthetic Data}
\label{subsec:methods:synthetic-data}

We expect CAKES to perform well as the cardinality of datasets increases, and to explore this scaling behavior, we augmented datasets in the ANN-benchmarks suite by adding random points within a 
small noise threshold of existing points. This allowed us to isolate the effect of \emph{cardinality} on the performance of CAKES 
from that of other factors such as dimensionality, metric, or topological structure of the dataset.

To elaborate, we start with an original dataset $X$ from the ANN-benchmark suite, a user-specified noise tolerance $\epsilon$, and a mutliplier $m$.
For each datum $x \in X$, we create $m$ new data points within a distance $\epsilon$ of $x$. To construct a synthetic data point $x'$, we choose $d$ random numbers 
$r_1, r_2, \cdots r_d$ in the interval $[-\tfrac{\epsilon}{\sqrt{d}}, \tfrac{\epsilon}{\sqrt{d}}]$ and then add them componentwise to the original datapoint. 
This ensures that any synthetic point is within a distance of $\epsilon$ from a real point in the original dataset.

### 2023-10-15 sections/3-datasets.tex
reworking data augmentation explanation

>>>>

In addition to benchmarks on datasets from the ANN Benchmarks suite, we also benchmarked on synthetic augmentations of these real datasets, using the process described in \ref{subsec:methods:synthetic-data}. In particular, we use a noise tolerance $\epsilon = 0.01$ and explore the scaling behavior as the multiplier $m$ of new points increases. While we explored the scaling behavior of CAKES with augmented versions of each dataset in \ref{table:datasets:summary}, we give an in-depth discussion of results for scaling behavior on fashion-mnist, glove-100, gist, and a purely random dataset.
